---
title: "R Notebook"
output: html_notebook
---

More and more, companies have data stored in Googlesheets. Maybe they are the results of a google survey or maybe it’s some google analytics data. The package googlesheets allows you to import data from googlesheets to R and also to manage data that is stored in a Googlesheet directly from R! The googlesheets package is actually a wrapper for the API, which makes it pretty easy/ straightforward.

```{r}
library(googlesheets)
library(tidyverse)
```

```{r}
gs_gap() %>% 
  gs_copy(to = "Gapminder")
```


```{r}
gap <- gs_title("Gapminder", verbose = FALSE)
```


```{r}
gap
```


```{r}
gs_ls()
```


```{r}
gap %>% gs_browse()
```


```{r}
africa <- gs_read(gap, ws="Africa")
```


```{r}
europe <- gs_read(gap, ws="Europe")
```


```{r}
glimpse(africa)
```


```{r}
glimpse(europe)
```


```{r}
library(httr)
genes <- GET(url= 'https://genelab-data.ndc.nasa.gov/genelab/data/search?term=space&from=0&type=cgene,nih_geo_gse&ffield=links&fvalue=GPL16417&ffield=Data%20Source%20Accession&fvalue=GSE82255&api_key=DWhP4gQqRT8DigPNex0eLM4zoXNcCLmLH8883UU31')
names(genes)
```


```{r}
genes_parsed <- content(genes, as='parsed', type = "application/json")
sapply(genes_parsed, class)
```


```{r}
sapply(genes_parsed$hits, class)
```


```{r}
library(jsonlite)
```


```{r}
genes_fromJSON <-fromJSON('https://genelab-data.ndc.nasa.gov/genelab/data/search?term=space&from=0&type=cgene,nih_geo_gse&ffield=links&fvalue=GPL16417&ffield=Data%20Source%20Accession&fvalue=GSE82255&api_key=DEMO_KEY')
sapply(genes_fromJSON, class)
```


```{r}
sapply(genes_fromJSON$hits, class)
```


```{r}
#content()
```


```{r}
metadata <- fromJSON("https://data.nasa.gov/data.json")
```


```{r}
class(metadata)
```


```{r}
sapply(metadata, class)
```


```{r}
names(metadata)
```


```{r}
names(metadata$dataset)
```


```{r}
glimpse(metadata$dataset)
```


```{r}
nasa_flat <- jsonlite::flatten(metadata$dataset)
class(nasa_flat)
```


```{r}
dim(nasa_flat)
```


```{r}
colnames(nasa_flat)
```


```{r}
class(nasa_flat)
```


```{r}
class(nasa_flat$keyword)
```


```{r}
nasa_keyword <- nasa_flat %>% 
  select(keyword, `_id.$oid`) %>% 
  unnest()

str(nasa_keyword)
```


```{r}
nasa_keyword %>% 
  group_by(keyword) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```


```{r}
library(rvest)
```


```{r}
url <- "https://www.amazon.com/Echo-2nd-Generation-speaker-Charcoal/product-reviews/B06XCM9LJ4/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&reviewerType=all_reviews&filterByStar=one_star&pageNumber=1" #URL for 1-star reviews

reviews <- read_html(url) 
```


```{r}
css <- ".review-text" 
nodes <- html_nodes(reviews, css)
text <- html_text(nodes)

text
```


```{r}
get_reviews <- function(url_base, i, css='.review-text'){
  x = vector()
  for (n in 1:i){
    reviews <- read_html(paste(url_base, n, sep=""))
    nodes <- html_nodes(reviews, css)
    text <- html_text(nodes)
    x <- c(x, text)
  }
  return(x)
}
```


```{r}
url_base <- "https://www.amazon.com/Echo-2nd-Generation-speaker-Charcoal/product-reviews/B06XCM9LJ4/ref=cm_cr_arp_d_viewopt_sr?ie=UTF8&reviewerType=all_reviews&filterByStar=one_star&pageNumber="

reviews <- get_reviews(url_base, 10)
```


```{r}
#library(readr)
reviews %>%
  as.data.frame() %>% #converting to dataframe
  write_csv('reviews.csv') #writing to csv
```


